---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

source("~/R/scrapper/tiktok/R/get_tt_user.R")
source("~/R/scrapper/tiktok/R/get_tt_posts.R")
```

## Tiktok scraping

**Needed to run:**

There are two working functions to scrape TikTok. 

- get_tt_user.R
- get_tt_posts.R

#### Get TikTok User

This function returns the account data for a specific user. Provide the function with a username/handle, and it will pull the data. 

```{r}
get_tt_user("addisonre") |> data.frame()
```

#### Get TikTok Posts

Given a url, the function returns relevant performance data for the post. 

```{r}
url <- "https://www.tiktok.com/@bmw/video/7462756650202483990?lang=en"
get_tt_posts(url) |> 
  data.frame()
```

With multiple urls, just use `purrr::map_dfr()` to return data for each video. 

#### Not working

The `get_tt_comments()` function is broken...

