---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("~/R/scrapper/threads/R/scrape_thread.R")
source("~/R/scrapper/threads/R/scrape_profile.R")
pacman::p_load(tidyverse, reticulate)
```

## Scraping Threads

In case there is ever a need, these functions use playwright to crawl the site. This is pretty basic, and to be honest, some of the times the post scraper actually grabs the wrong thread. 

### Scraping a thread 

The thread returns a named list - thread_data and replies data. There isn't a whole lot that's returned by Threads, and this tries to get the relevant info. 

```{r}
dat <- scrape_thread(url = "https://www.threads.net/@koreydior_/post/DFRXN-kt1H9")

list(dat$thread_data, dat$replies_data[1:4,])
```

It is possible to scrape multiple threads, but the replies data doesn't have a way of identifying which post the reply is being made to. So running across multiple threads can be a little difficult. 

To do so, it could be done like this: 

```{r, eval = FALSE}
urls <- c("https://www.threads.net/@natgeo/post/DFSt1c2soIH",
          "https://www.threads.net/@natgeo/post/DFPwfxNt-Fv")

# Apply safe_scrape_thread to the list of URLs
results <- map(urls, scrape_thread)

# Filter out failed results
results <- compact(results)

# Combine the results
all_threads <- map_df(results, ~.x$thread_data)
all_replies <- map_df(results, ~.x$replies_data) # may want to keep replies in separate lists 
```

### Scraping the user profile 

The user profile scraper returns a named list - profile_data and recent_threads. The user data is basic, the threads looks to be the 30 most recent threads posted from that account. 

```{r}
dat <- scrape_profile(url = "https://www.threads.net/@natgeo/")

list(dat$profile_data, dat$recent_threads[1:3,])
```
